\documentclass[a4paper,10pt]{article}

\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=2pt}

% Section styling (Jake-style)
\titleformat{\section}{
    \large\bfseries
}{}{0em}{}[\titlerule]

% Custom commands
\newcommand{\name}[1]{\centerline{\huge \bfseries #1}}
\newcommand{\contact}[1]{\centerline{\small #1}}

\newcommand{\subheading}[4]{
    \textbf{#1} \hfill #2 \\
    \textit{#3} \hfill \textit{#4} \\
}

\newcommand{\projectheading}[1]{
    \vspace{2pt}
    \textbf{#1}
}

\begin{document}

%----------------------------------------------------------------------------------------
% HEADER
%----------------------------------------------------------------------------------------

\name{Omkar Sathe}
\contact{Mumbai, India \quad | \quad +91 7506 384976 \quad | \quad \href{mailto:work.omkar@outlook.com}{work.omkar@outlook.com}}
\contact{\href{https://linkedin.com/in/omkarsathe2211}{linkedin.com/in/omkarsathe2211} \quad | \quad \href{https://github.com/OmkarSS-22}{github.com/OmkarSS-22}}

\vspace{4pt}

%----------------------------------------------------------------------------------------
% SUMMARY
%----------------------------------------------------------------------------------------

\section*{Summary}

Full-Stack MERN Engineer with 3 years of experience building configurable workflow systems, reusable UI libraries, and production-grade automation platforms. Designed a drag-and-drop invoice workflow engine using React Flow and architected modular backend/frontend systems distributed internally as Node.js packages. Experienced in scalable API design, system modularization, and CI/CD-driven cloud and on-prem deployments.

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------

\section*{Experience}

\subheading
{SequelString AI Pvt. Ltd.}{Jul 2023 -- Present}
{Jr. Full Stack Developer (MERN)}{Mumbai, India}

\projectheading{Automated Invoice Processing Platform (Sole Developer)}
\begin{itemize}
    \item Designed and developed a configurable invoice automation engine with dynamic workflow configuration and rule-based validation.
    \item Built a drag-and-drop node-based process builder using React Flow for visual workflow creation.
    \item Architected RESTful backend services with SAP API integrations, scheduled processing using node-cron, and real-time updates using Server-Sent Events (SSE).
    \item Modularized system into reusable frontend and backend Node.js libraries for internal use.
\end{itemize}

\projectheading{Reusable UI Component Library}
\begin{itemize}
    \item Designed and maintained a centralized internal React component library used across multiple projects.
    \item Built reusable date components and chart components (pie, bar, line, composite).
    \item Standardized UI patterns, improving consistency and development velocity.
\end{itemize}

\projectheading{Vendor \& Order Management System}
\begin{itemize}
    \item Implemented procurement workflows including automated three-way matching (PO, Invoice, GRN).
    \item Designed MongoDB schemas for reconciliation tracking and transactional consistency.
    \item Reduced reconciliation errors by 40\% and improved API response times by ~1.5 seconds.
\end{itemize}

\projectheading{Sequel Expense (Project Lead \& Full-Stack Developer)}
\begin{itemize}
    \item Led a team of 4 developers to build an enterprise expense management system with multi-level approval workflows.
    \item Designed role-based access control and approval state-machine logic.
    \item Delivered 6+ features per sprint under Agile methodology, improving client efficiency by 50\%.
\end{itemize}

\projectheading{Infrastructure \& Deployment}
\begin{itemize}
    \item Designed and maintained CI/CD pipelines using Docker and GitHub Actions for cloud and on-prem deployments.
\end{itemize}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\section*{Education}

\textbf{University of Mumbai} \hfill Apr 2023 \\
Bachelor of Engineering - Electronics and Telecommunication \\
GPA: 7.5/10.0 \hfill Mumbai, India

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------

\section*{Skills}

\textbf{Core Stack:} Node.js, Express.js, React.js, MongoDB, TypeScript, JavaScript (ES6+) \\
\textbf{UI \& Visualization:} React Flow, react-chartjs-2, Component Libraries, Chakra UI, Material UI, Tailwind CSS \\
\textbf{Backend \& Architecture:} REST APIs, GraphQL, Node.js Package Development, Workflow Engines, Rule-Based Validation, Third-Party API Integration, JWT, OAuth2.0, RBAC \\
\textbf{DevOps:} Docker, GitHub Actions (CI/CD), Azure Functions, Nginx \\
\textbf{Tools:} Git, Postman, VS Code, Figma \\
\textbf{Operating Systems:} Linux (Fedora)

\end{document}