\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage{inputenc}
\usepackage[scale=0.93]{geometry}
\usepackage{tabularx}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\usepackage{enumitem}
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=4mm}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

% Fix name overlapping by redefining title block
\renewcommand*{\makecvtitle}{%
  \begin{center}
    {\Huge\bfseries Omkar Sathe}\\[1mm] % Adjust spacing here if needed
  \end{center}
}

\renewcommand*{\labelitemi}{-}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand*{\experienceentry}[5][1mm]{
    \subsection{#2} \vspace{-1mm}
    \begin{tabularx}{\textwidth}{LR}
        {\itshape #3} & {\itshape #4, #5}
    \end{tabularx}
    \par\addvspace{#1}
}

\newcommand*{\educationentry}[4][0.5mm]{
    \begin{tabularx}{\textwidth}{LR}
        {\bfseries #3} & {\bfseries #4} \\
    \end{tabularx}
    {\itshape #2}
    \par\addvspace{#1}
}

\begin{document}

\makecvtitle
\vspace{-6mm}

% Contact row - add spacing to prevent overlap
\begin{tabularx}{\textwidth}{C C C}
    \emailsymbol\enspace \emaillink{work.omkar@outlook.com} 
    & \mobilephonesymbol\enspace (+91) 7506 384976 
    & \faLinkedin\enspace \href{https://www.linkedin.com/in/omkarsathe2211}{linkedin.com/in/omkarsathe2211}
\end{tabularx}

\vspace{1mm}

\begin{center}
\faGithub\enspace \href{https://github.com/OmkarSS-22}{github.com/OmkarSS-22}
\end{center}

\vspace{-3mm}

\section{SUMMARY}
Backend-focused Full-Stack Developer with 2 years of experience building secure, scalable systems using Node.js, Express, AWS SDK, and MongoDB. Strong expertise in REST API development, async workflows, cron jobs, authentication, server-to-server communication, and distributed automation pipelines.

\vspace{-3mm}

\section{EXPERIENCE}
\experienceentry{SequelString AI Pvt. Ltd.}{Jr. Full Stack Developer (MERN)}{Jul 2023 - Present}{Mumbai, India}

\textbf{Automated Invoice Processing (Sole Backend Developer)}
\begin{itemize}
    \item Built secure, scalable REST APIs using Node.js \& Express, following HTTP best practices.
    \item Integrated AWS services via AWS SDK for document upload, retrieval, and archival in S3.
    \item Developed automated async workflows using Promises, callbacks, throttling, and retry logic.
    \item Designed and scheduled cron jobs for workflow cycles, batching, and rule-based validations.
    \item Implemented JWT authentication and OAuth2 integrations (Microsoft Graph, AWS, external vendors).
    \item Built multi-step validation pipelines reducing manual work by 50 to 60\%.
    \item Added robust error handling with auto-retry, and monitoring logs.
    \item Optimized performance via caching and async orchestration strategies.
\end{itemize}

\textbf{Vendor \& Order Management}
\begin{itemize}
    \item Built procurement workflow features including three-way matching (PO, Invoice, GRN), reducing reconciliation errors by 40\%.
\end{itemize}

\textbf{Sequel Expense (Project Lead)}
\begin{itemize}
    \item Led a team of four to build an expense management system with approval workflows, improving efficiency by 50\%.
\end{itemize}

\textbf{Miscellaneous Projects}
\begin{itemize}
    \item Enhanced API performance by 1.5s and reduced bug resolution time by 30\%.
\end{itemize}

\textbf{Infrastructure \& Deployment}
\begin{itemize}
    \item Set up CI/CD pipelines with Docker \& GitHub Actions and deployed services on Azure Functions and on-premise environments.
\end{itemize}

\vspace{-3mm}

\section{SKILLS}
\begin{tabularx}{\textwidth}{>{\bfseries}l@{\hskip 3mm}L}
Backend & Node.js, Express.js, REST APIs, Cron Jobs, AWS SDK, SMTP, SFTP, MS Graph APIs, Google APIs, OAuth2, SSE, Server-to-Server Integrations \\
Frontend & React.js, Tailwind CSS, Material UI, Chakra UI \\
Languages & JavaScript, TypeScript, HTML5, CSS3 \\
Database & MongoDB \\
DevOps & Docker, GitHub Actions, Azure Functions \\
Tools & Postman, Figma, VS Code \\
Soft Skills & Problem Solving, Teamwork, Attention to Detail, Ownership
\end{tabularx}

\vspace{-3mm}

\section{EDUCATION}
\educationentry{Bachelor of Engineering - Electronics \& Telecom}{University of Mumbai — Apr 2023}{Mumbai, India}
GPA: 7.5/10.0

\end{document}
