\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage{inputenc}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\renewcommand*{\labelitemi}{-}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand*{\experienceentry}[5][1.5mm]{
    \subsection{#2} \vspace{-1.5mm}
    \begin{tabularx}{\textwidth}{LR}
        {\itshape #3} & {\itshape #4, #5}
    \end{tabularx}
    \par\addvspace{#1}
}

\newcommand*{\educationentry}[4][0.5mm]{
    \begin{tabularx}{\textwidth}{LR}
        {\bfseries #3} & {\bfseries #4} \\
    \end{tabularx}
    {\itshape #2}
    \par\addvspace{#1}
}

\newcommand*{\scoreentry}[3][2.5mm]{
    {\bfseries #2} \\
    {\itshape #3}
    \par\addvspace{#1}
}

\firstname{Omkar}
\familyname{Sathe}
\address{Mumbai, India}{}

\begin{document}
\maketitle
\vspace{-9.0mm}
\begin{tabularx}{\textwidth}{C C C}
    \emailsymbol\enspace \emaillink{work.omkar@outlook.com} & \mobilephonesymbol\enspace (+91) 7506 384976 & \faLinkedin\enspace \href{https://www.linkedin.com/in/omkarsathe2211}{linkedin.com/in/omkarsathe2211} 
\end{tabularx}
% \vspace{-0.5mm}

\begin{center}
\faGithub\enspace \href{https://github.com/OmkarSS-22}{https://github.com/OmkarSS-22}
\end{center}
\vspace{-4.0mm}

\section{SUMMARY}
Full-Stack Developer adept in developing scalable web applications using MERN stack. Passionate about delivering high-quality, user-centric products in a fast-paced environment, I blend technical proficiency with strategic leadership to achieve exceptional results.

% \vspace{1.0mm}

\vspace{-4.0mm}

% \begin{minipage}[t]{0.35\textwidth}

% \section{LANGUAGES}
% \begin{itemize}
%     \item English (Native or Bilingual)
%     \item Marathi (Native)
%     \item Hindi (Native)
% \end{itemize}

% \section{INTERESTS}
% \begin{itemize}
%     \item Books
%     \item Music
%     \item Trekking/Hiking
% \end{itemize}

% \end{minipage}
\hfill
% \begin{minipage}[t]{0.62\textwidth}

\section{EXPERIENCE}
\experienceentry{SequelString AI Pvt. Ltd.}{Jr. Full Stack Developer (MERN)}{Jul 2023 - Present}{Mumbai, India}

\textbf{Automated Invoice Processing (Sole Developer)}
\begin{itemize}
    \item Designed and developed a fully automated invoice processing module, enabling custom workflows and integrating with SAP, cloud, and local storage. Implemented API-based extraction and custom validation, reducing manual effort by 50\% and improving efficiency by 60\%.
\end{itemize}
\vspace{1.0mm}

\textbf{Vendor and Order Management (Full-Stack Developer)}
\begin{itemize}
    \item Developed and optimized features for procurement workflows, implementing three-way matching (PO, Invoice, GRN), reducing reconciliation errors by 40\%, and improving system efficiency by 30\%.
\end{itemize}
\vspace{1.0mm}

\textbf{Sequel Expense (Project Lead and Full-Stack Developer)}
\begin{itemize}
    \item Led a team of three in building an expense management application with approval workflows, increasing processing efficiency by 50\%. Managed agile development, delivering six features per sprint.
\end{itemize}
\vspace{1.0mm}

\textbf{Miscellaneous Projects (Full Stack Developer)}
\begin{itemize}
    \item Contributed across domains, optimizing performance, improving API response times by 1.5s, and reducing bug resolution time by 30\%.
\end{itemize}
\vspace{-2.0mm}

\section{EDUCATION}
\educationentry{Bachelor of Engineering - Eelec. and Telecom.}{University of Mumbai - Apr '23}{Mumbai, India}
GPA: 7.5/10.0
\par
% \end{minipage}

\vspace{-2.0mm}

\section{SKILLS}
\begin{tabularx}{\textwidth}{>{\bfseries}l@{\hskip 3.5mm}L}
Back End & Node.js, Express.js \\
Frontend & React.js, Material UI, Chakra UI, Tailwind CSS \\
Languages & JavaScript (ES6+), TypeScript, HTML5, CSS3 \\
DBMS & MongoDB \\
OS & Linux(Fedora) \\
DevOps and Tools & Git, GitHub, Docker, Azure Functions, REST APIs, Postman \\
Misc. & VsCode, Figma \\
Soft-skills & Attention to Detail, Teamwork, Empathy and User-Centric Thinking, Project
Management Skills
\end{tabularx}


\end{document}
