\documentclass[10pt,a4paper]{moderncv}
\moderncvtheme[blue]{banking}
\nopagenumbers{}

\usepackage[T1]{fontenc}
\usepackage{inputenc}
\usepackage[scale=0.93]{geometry}
\usepackage{tabularx}
\usepackage{helvet}
\usepackage{enumitem}

\renewcommand{\familydefault}{\sfdefault}
\renewcommand*{\labelitemi}{-}

\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=4mm}
\linespread{0.97}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

\newcommand*{\experienceentry}[4]{
    \subsection{#1}
    \begin{tabularx}{\textwidth}{LR}
        {\itshape #2} & {\itshape #3, #4}
    \end{tabularx}
    \vspace{0.5mm}
}

\newcommand*{\educationentry}[3]{
    \begin{tabularx}{\textwidth}{LR}
        {\bfseries #1} & {\bfseries #2} \\
    \end{tabularx}
    {\itshape #3}
}

\firstname{Omkar}
\familyname{Sathe}
\address{Mumbai, India}{}
\email{work.omkar@outlook.com}
\mobile{+91 7506 384976}
\social[linkedin]{omkarsathe2211}
\social[github]{OmkarSS-22}

\begin{document}
\maketitle
% \vspace{-10mm}

% \begin{tabularx}{\textwidth}{C C C}
%     \emailsymbol\enspace \emaillink{work.omkar@outlook.com} & 
%     \mobilephonesymbol\enspace (+91) 7506 384976 & 
%     \faLinkedin\enspace \href{https://www.linkedin.com/in/omkarsathe2211}{linkedin.com/in/omkarsathe2211}
% \end{tabularx}

% \begin{center}
% \faGithub\enspace \href{https://github.com/OmkarSS-22}{github.com/OmkarSS-22}
% \end{center}

\section{SUMMARY}
Full-Stack MERN Engineer with 2+ years of experience building configurable workflow systems, reusable UI libraries, and production-grade automation platforms. Designed a drag-and-drop invoice workflow engine using React Flow and architected modular backend/frontend systems distributed internally as Node.js packages. Experienced in scalable API design, system modularization, and CI/CD-driven cloud and on-prem deployments.

\section{EXPERIENCE}

\experienceentry
{SequelString AI Pvt. Ltd.}
{Jr. Full Stack Developer (MERN)}
{Jul 2023 - Present}
{Mumbai, India}

\textbf{Automated Invoice Processing Platform (Sole Developer)}
\begin{itemize}
    \item Designed and developed a configurable invoice automation engine with dynamic workflow configuration and rule-based validation.
    \item Built a drag-and-drop node-based process builder using React Flow for visual workflow creation.
    \item Architected RESTful backend services with SAP API integrations, scheduled processing using node-cron, and real-time status updates using Server-Sent Events (SSE).
    \item Split the system into independently maintainable frontend and backend Node.js libraries for internal reuse.
    \item Reduced manual effort by 50\% and improved efficiency by 60\%; deployed via Docker, GitHub Actions, and Azure Functions across cloud and on-prem environments.
\end{itemize}

\textbf{Reusable UI Component Library}
\begin{itemize}
    \item Designed and maintained a centralized internal React component library adopted across organization projects.
    \item Built reusable date components (react-date-range) and graph components (react-chartjs-2: pie, bar, line, composite).
    \item Standardized UI patterns, improving consistency and accelerating development velocity.
\end{itemize}

\textbf{Vendor \& Order Management System}
\begin{itemize}
    \item Implemented procurement workflows including automated three-way matching (PO, Invoice, GRN).
    \item Designed MongoDB schemas for reconciliation tracking and transactional consistency.
    \item Reduced reconciliation errors by 40\% and improved API response times by ~1.5 seconds.
\end{itemize}

\textbf{Sequel Expense (Project Lead \& Full-Stack Developer)}
\begin{itemize}
    \item Led a team of 4 developers in building an enterprise expense management system with multi-level approval workflows.
    \item Designed role-based access control and approval state-machine logic.
    \item Delivered 6+ features per sprint under Agile methodology, increasing client processing efficiency by 50\%.
\end{itemize}

\section{EDUCATION}

\educationentry
{University of Mumbai - Apr '23}
{Mumbai, India}
{Bachelor of Engineering - Electronics and Telecommunication \quad | \quad GPA: 7.5/10.0}

\section{SKILLS}

\begin{tabularx}{\textwidth}{>{\bfseries}l@{\hskip 3mm}X}
Core Stack & Node.js, Express.js, React.js, MongoDB, TypeScript, JavaScript (ES6+) \\
UI \& Visualization & React Flow, react-chartjs-2, Component Library Design, Chakra UI, Material UI, Tailwind CSS \\
Backend \& Architecture & REST APIs, GraphQL, Node.js Package Development, Workflow Engines, Rule-Based Validation, TP API Integration, Authentication (JWT, OAuth2.0), Role-Based Access Control (RBAC) \\
DevOps & Docker, GitHub Actions (CI/CD), Azure Functions \\
Tools & Git, Postman, VS Code, Figma \\
Operating Systems & Linux (Fedora) \\
\end{tabularx}

\end{document}